---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, message=FALSE}
library(data.table)
library(purrr)
library(dplyr)
library(ggplot2)
library(gganimate)
library(extrafont)
library(RColorBrewer)
library(pals)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, dev = "svg")
knitr::opts_knit$set(root.dir = "C:\\Users\\darkg\\Desktop\\Homework Scans\\2020Sm_ART167\\newsletter\\issue1")
loadfonts(device = "win")
```

## Single Trial
```{r}
tosses = 250
p = 0.5

set.seed(1)
trial = sample.int(2, tosses, replace = TRUE, prob = c(1-p, p)) - 1

results = list()
for(i in seq_along(trial)){
  results[[i]] = as.data.frame.list(table(trial[1:i]))
}

data = rbindlist(results, fill=TRUE) %>%
  setNames(c("Heads", "Tails")) %>% 
  cbind("tosses" = 1:tosses) %>%
  mutate(Heads = Heads / tosses, Tails = Tails / tosses) %>%
  melt(id.vars = "tosses", variable.name = "outcome", value.name = "proportion")
```

```{r}
g = ggplot(data, aes(x = outcome, y = proportion, group = outcome)) +
  geom_bar(stat = "identity", aes(fill = outcome), show.legend = FALSE) +
  labs(subtitle = "Tosses = {closest_state}",
       x = "\nOutcome",
       y = "Proportion\n",
       fill = "") +
  scale_fill_manual(values = brewer.pal(n = 10, name = "Spectral")[c(2,9)]) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(colour = "#808080"),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size=12),
        axis.text = element_text(size=11),
        text = element_text(family = "CMU Serif")) +
  transition_states(tosses, transition_length = 0.5, state_length = 0, wrap = TRUE)

animate(g, fps = 20, nframes = 250, res=100)
anim_save("single_coin.gif")
```


## Sampling Distribution
```{r}
coins = 1e4
p = 0.5

results = list()
for(i in 1:20){
  tosses = 50*i
  results[[i]] = data.table(1:coins, replicate(coins, sum(sample.int(n=2, size=tosses, replace=TRUE, prob=c(1-p, p)) - 1)/tosses)) %>%
    setNames(c("idx", as.character(50*i)))
}

data = reduce(results, merge, by = "idx") %>% 
  melt(id.vars = "idx", variable.name = "tosses", value.name = "p_hat")
```

```{r}
g = ggplot(data, aes(x = p_hat, group = tosses)) +
  geom_density(aes(color = as.numeric(tosses), fill = as.numeric(tosses)), size = 2, alpha = 0.75, show.legend = FALSE) +
  labs(title = "Coins = 1e4",
       subtitle = "Tosses = {closest_state}",
       x = expression(hat(p)),
       y = "Density\n") +
  scale_color_gradientn(colors = cubehelix(n = 255, r = -1.5, hue = 2, gamma = 0.8)[25:220]) +
  scale_fill_gradientn(colors = cubehelix(n = 255, r = -1.5, hue = 2, gamma = 0.8)[25:220]) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(colour = "#808080"),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size=12),
        axis.text = element_text(size=11),
        text = element_text(family = "CMU Serif")) +
  transition_states(tosses, transition_length = 1, state_length = 1, wrap = TRUE)

animate(g, fps = 30, nframes = 150, res=100)
anim_save("sampling_distribution.gif")
```


## Multiple coins
```{r}
LLN = function(coins, tosses, p){
  dt = replicate(coins, sample(c(0,1), tosses, replace = TRUE, prob = c(1-p, p))) %>% as.data.table()
  dt = cbind(tosses = 1:tosses, map_df(dt, ~cumsum(.x)/1:tosses)) %>% setNames(c("tosses", paste("coin", 1:coins, sep="")))
  return(dt)
}

coins = 10
tosses = 1000
p = 0.5

data = LLN(coins, tosses, p) %>% melt(id.vars = "tosses", variable.name = "coin", value.name = "proportion")
```

```{r}
g = ggplot(data, aes(x = tosses, y = proportion)) + 
  geom_line(aes(color = coin), size = 1.5, alpha = 0.75) + 
  scale_color_brewer(palette="Spectral") + 
  coord_cartesian(ylim = c(0,1)) +
  labs(title = "Multiple Coins",
       subtitle = "Coins = 10",
       x = "\nTosses",
       y = "Proportion\n",
       col = "") +
  theme(panel.grid.major = element_line(colour = "grey"),
        panel.background = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title = element_text(hjust = 0.5, size=12),
        axis.text = element_text(size=11),
        legend.position=c(0.525,0.15),
        legend.direction = "horizontal",
        legend.box = "horizontal")

g1 = g + transition_reveal(tosses)

animate(g1, width = 480, height = 480, fps = 40, nframes = 1000, res=100)
anim_save("multi_coin.gif")
```

```{r}
data$tosses = as.factor(data$tosses)

g = ggplot(data, aes(x = proportion, group = tosses)) + 
  stat_density(aes(color = as.numeric(tosses), fill = as.numeric(tosses)),
               size = 2, alpha = 0.75, geom = "area", position = "identity", show.legend = FALSE) +
  labs(title = " ",
       subtitle = " ",
       x = "",
       y = "Density\n") +
  # scale_color_distiller(palette = "RdYlBu") +
  # scale_fill_distiller(palette = "RdYlBu") +'
  scale_color_gradientn(colours=matlab.like(1000)) +
  scale_fill_gradientn(colours=matlab.like(1000)) +
  coord_flip() +
  theme(panel.grid.major = element_line(colour = "grey"),
